Machine Learning Methods for Site-specific Input Management

### 2022-02-07 Codes/PrepareResults.rmd

data_sf <- st_read(here("Shared/Data/snider_high_res.gpkg")) %>%
    na.omit() %>%
    dplyr::rename(tgtn=NPlan,tgts=SRPlan)

data_dt <- data.table(data_sf) %>%
    setnames(names(.),tolower(names(.)))

tgts_ls <- data_dt[,tgts] %>% unique() %>% sort

ctree_data <- copy(data_dt) %>%
  .[tgts %in% tgts_ls[1:2],] %>%
  .[,treat:=ifelse(tgts==tgts_ls[2],1,0)] %>%
  #--- Corn Yield: 1 bu/acre ->  62.77 kg/ha---#
  .[,yield:= yield*62.77]

tree <- causalTree(
  yield ~ slope+ecs,
  data = ctree_data,
  treatment = ctree_data$treat,
  split.Rule = "CT",
  cv.option = "CT",
  split.Honest = T,
  cv.Honest = T,
  split.Bucket = F,
  xval = 5,
  cp = 0,
  minsize = 20,
  propensity = 0.5
)

opcp <- tree$cptable[,1][which.min(tree$cptable[,4])]
opfit <- prune(tree, opcp)

@@

# Prepare sample field data set by plot, subplot, and cell resolution (one-time run)

```{r}
# source("./GitControlled/Codes/0_1_functions_gen_analysis_data.R")

# pCorn <- price_table[2, pCorn]
# pN <- price_table[2, pN]

# /*=================================================*/
#' # Field Data Sets
# /*=================================================*/

#/*----------------------------------*/
#' ## (1) cell-level data set 
#/*----------------------------------*/
# + NOTE: I needed to do the following things, because the existing raw data does not have m_error
# field <- readRDS(here("Shared/Data/for_Simulations/field_padding.rds"))

# coef_data <- readRDS(here("Shared/Data/for_Simulations/coefficients_sprange_400.rds"))

# x=1
# coef_data_m <- coef_data[sim == x, ]
# coef_data_t <- coef_data[sim == ifelse(x + 1 >= max(sim), 1, x + 1), ]

# sample_dt_cell <- prepare_raw_data(x, field=field, coef_data_m=coef_data_m, coef_data_t=coef_data_t, app_error="no") %>%
#   .$reg_raw_data

# field_cell_sf <- 
#   left_join(select(field, unique_cell_id), field_cell_dt, by="unique_cell_id")%>%
#     na.omit() %>%
#     mutate(plot_id = ceiling(subplot_id/4)) %>%
#     filter(padding==1)

# saveRDS(field_cell_sf, here("Shared/Results/for_writing/sample_field_cell_sf.rds"))

#/*----------------------------------*/
#' ## (2) subplot-level field without padding area 
#/*----------------------------------*/

# field_subplot_sf <- 
#   field_cell_sf %>%
#   group_by(subplot_id, strip_id) %>%
#   summarise(
#     sim = mean(sim),
#       yield = mean(yield),
#       opt_N = mean(opt_N),
#       rate = mean(rate),
#       aa_n = mean(aa_n), 
#       alpha = mean(alpha),
#       beta = mean(beta),
#       ymax = mean(ymax),
#       alpha1 = mean(alpha1),
#       alpha2 = mean(alpha2),
#       beta1 = mean(beta1),
#       beta2 = mean(beta2),
#       ymax1 = mean(ymax1),
#       ymax2 = mean(ymax2),
#       theta_1 = mean(theta_1),
#       theta_2 = mean(theta_2)
#   ) %>%
#   mutate(unique_subplot_id = paste0(strip_id,"_",subplot_id))%>%
#   select(!c(strip_id, subplot_id))

# saveRDS(field_subplot_sf, here("Shared/Results/for_writing/sample_field_subplot_sf.rds"))

#/*----------------------------------*/
#' ## (3) plot-level dataset without padding area  
#/*----------------------------------*/
# field_plot_sf <- field_cell_sf%>%
#     group_by(plot_id, strip_id, rate)%>%
#     summarise()

# saveRDS(field_plot_sf, here("Shared/Results/for_writing/sample_field_plot_sf.rds"))
```

>>>>

data_sf <- st_read(here("Shared/Data/snider_high_res.gpkg")) %>%
  na.omit() %>%
  dplyr::rename(tgtn = NPlan, tgts = SRPlan)

data_dt <- data.table(data_sf) %>%
  setnames(names(.), tolower(names(.)))

tgts_ls <- data_dt[, tgts] %>%
  unique() %>%
  sort()

ctree_data <- copy(data_dt) %>%
  .[tgts %in% tgts_ls[1:2], ] %>%
  .[, treat := ifelse(tgts == tgts_ls[2], 1, 0)] %>%
  #--- Corn Yield: 1 bu/acre ->  62.77 kg/ha---#
  .[, yield := yield * 62.77]

tree <- causalTree(
  yield ~ slope + ecs,
  data = ctree_data,
  treatment = ctree_data$treat,
  split.Rule = "CT",
  cv.option = "CT",
  split.Honest = T,
  cv.Honest = T,
  split.Bucket = F,
  xval = 5,
  cp = 0,
  minsize = 20,
  propensity = 0.5
)

opcp <- tree$cptable[, 1][which.min(tree$cptable[, 4])]
opfit <- prune(tree, opcp)

@@
